### 2020-03-24 report/report/report.tex
update

>>>>

  \subsection{Spin Experiment 4,5,6, pi\_corpse}
  These experiments were intended to build a CORPSE $R_{x}(\pi)$ pulse
  following this Ken Brown paper \cite{merrill2014progress}.

  \subsection{Spin Experiment 7}
  This experiment is the same as experiment 0 with the added constraint of
  zero integration.

  \section{Amplitude Robustness}

  \subsection{Cavity Experiment 0}
  0 to 2 in the cavity following \cite{heeres2017implementing}.
